### 2018-05-07 acknowledge.tex
Fix Typos

The ultimate success of the work presented in this thesis would not have been possible without the continued time and support of numerous individuals I've encounters throughout my life and career.

>>>>

The ultimate success of the work presented in this thesis would not have been possible without the continued investment of time and support from numerous individuals I've encountered throughout my life and career.
